---
title: "Bobcatsss 2020 summary"
author: "Remigiusz Żulicki, Michał Żytomirski"
date: "22 01 2020"
output: rmarkdown::github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
df_md <- read_csv("df_final.csv")
df_long_md <- read_csv("df_long_final.csv")
```

## Distribution of domains vs order in set of search results vs browser mode

28 unique domains

```{r domain_ord_mode_count, echo=FALSE, fig.height=10, fig.width=8}
df_long_md <- df_long_md %>% 
  mutate(browser_mode = factor(browser_mode)) %>%
  mutate(browser_mode = forcats::fct_recode(
    .f = browser_mode,
    `normal search` = "normal",
    `incognito search` = "incognito"))

ggplot(df_long_md, aes(x = fct_rev(fct_infreq(url_top_domain)),
                       fill = ordered(search_order_short))) +
  geom_bar() + facet_grid(rows = vars(browser_mode)) +
  coord_flip() +
  labs(x = 'Top domain',
       y = 'Url count [n = 730]',
       caption = "Source: own research") +
  scale_fill_ordinal(name = "Order in set of search results") +
  theme(legend.position = "bottom")
```

## What is a set of search results (SSR)?

First five organic Google search results (top domains!) encoded as single characters

Most common example:

```{r ivl3o, echo=FALSE}
knitr::kable(
  df_long_md %>% 
               filter(letter_top_domain %in% c("I", "V", "B", "3", "1")) %>% 
    select(letter_top_domain, url_top_domain) %>% 
    distinct() %>% 
    rename(`Top domain` = "url_top_domain",
         `Single character encoding` = "letter_top_domain"),
  caption = "Source: own research")
  
```

## SSR distribution vs browser mode

50 SSRs in normal mode - 37 of 73 participants saw a unique SSR
51 SSRs in incognito mode - 38 of 73 participants saw a unique SSR

**More than a half of participants saw a unique set of results**

```{r search_res_mode_count, echo=FALSE, fig.height=10, fig.width=8}
df_md %>% gather(incognito, normal, key = "browser_mode", value = "search_res") %>%
  mutate(browser_mode = factor(browser_mode)) %>%
  mutate(browser_mode = forcats::fct_recode(
    .f = browser_mode,
    `normal search` = "normal",
    `incognito search` = "incognito")) %>% 
  ggplot(aes(x = search_res %>% fct_infreq() %>% fct_rev(), fill = browser_mode)) + 
  geom_bar(position = "dodge") +
  facet_grid(col = vars(browser_mode)) +
  coord_flip() +
  labs(x = 'Set of search results (SSR)',
       y = 'Participant count [n = 73]',
       caption = "Source: own research") +
  guides(fill = "none")
```

## Measuring difference between normal and private search

Optimal string alignment distance(OSA) adapted from Mark P.J. van der Loo https://journal.r-project.org/archive/2014-1/loo.pdf 

- substitution of a character: ‘foo’→‘boo’.
- deletion of a character: ‘foo’→‘oo’.
- insertion of a character: ‘foo’→‘floo’.
- transposition of two adjacent characters: ‘foo’→‘ofo’.

Each of weight 1.

In out case OSA must be an integer, between 0 (no difference) and 5

**29 of 73 participants saw the same SSR (OSA = 0) in both private and incognito search. Even more - 36 of 73 - saw just a permutation**.

```{r osasummary, include=FALSE, echo=FALSE}
summary(df_md$dist_osa)
table(df_md$dist_osa)
table(df_md$is_incognito_permutation_of_normal)
table(df_md$dist_osa, df_md$is_incognito_permutation_of_normal)
```
```{r osadistrib, echo=FALSE, fig.height=8, fig.width=8}
ggplot(df_md) +
  geom_bar(aes(x = ordered(dist_osa), fill = is_incognito_permutation_of_normal)) +
  labs(x = 'OSA - normal vs private search',
       y = 'Participant count [n = 73]',
       caption = "Source: own research") +
  scale_fill_discrete(name = "Were the difference just a permutation?",
                      labels = c("No", "Yes")) +
  theme(legend.position = "bottom")
```

## In search for independent variables

**The difference (OSA distance) between normal and private search was lower for participant with less personalized search result sets in normal search**

```{r dist_osa_by_normal_count_plot, echo=FALSE, fig.width=8}
ggplot(df_md, aes(x = normal_count > 2, y = dist_osa)) + 
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center",
               binwidth = 1/5,
               alpha = 3/4,
               aes(fill = ordered(dist_osa),
                   colour = ordered(dist_osa))) +
  labs(x = "SSR in normal search > 2",
       y = 'OSA',
       subtitle = "Less personalized SSR means that more than 2 participants saw it",
       caption = "Source: own research") +
  guides(fill = "none", colour = "none") +
  scale_x_discrete(labels = c("No", "Yes"))
```

*W* = 697.5, *p* < 0.05, *r* = -0.252 (*effect size* small to medium).
